Graph Neural Networks For Multi-Image Matching

### 2019-09-23 latex/iclr2020/main.tex
figures updated

\begin{figure}[t]
\begin{subfigure}[b]{.45\linewidth}
  \centering
  \includegraphics[width=0.95\linewidth]{figures-UniverseOfFeatures-v2.pdf}
  \caption{Illustration of the universe of features.}
  \label{fig:1a}
  \label{fig:universefeatures}
\end{subfigure}%
\begin{subfigure}[b]{.45\linewidth}
  \centering
  \includegraphics[width=0.95\linewidth]{figures-GeometricConsistency-v2.pdf}
  \caption{Illustrated here is an example of how the geometric loss is computed for one feature.}
  \label{fig:1b}
  \label{fig:geoconsist}
\end{subfigure}
\caption{
  \textbf{(a)} Each feature in each image corresponds to a 3D point in the scene.
  We can construct cycle consistent embeddings of the features by mapping each one to the one-hot vector of its corresponding 3D point.
  While there can be many features, there are fewer 3D points and thus this corresponds to a low rank factorization of the correspondence matrix.
  \textbf{(b)} Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
  The epipolar line is the line of projection of the feature on the first image, projected onto to the second.
  The distance to this line on the second image indicates how likely that point is to correspond geometrically to the original feature.
  There can be false positives along the projected line, as shown by the square feature in the figure, but other points will be eliminated, such as the hexagonal feature.
  Best viewed in color.
}
\label{fig:1}
\end{figure}

@@

This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
We try to learn vertex embeddings $\mF_V$ to approximate $\mX$ - in other words the final embedding should be an encoding of the universe of features.
As we do not have the ground truth matches $\mM$, we approximate it using the noisy adjacency matrix $\mA$ of our correspondence graph. Thus our loss would be 
\begin{equation}
\mathcal{L}(\mA, \mF_V) = \mathcal{D}(\mA, \mF_V \mF_V^\top)
\end{equation}
Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss. 
Note that because of this formulation, we can determine our embeddings only up to a rotation, as
$ \mE R(\mE R)^\top
= \mE RR^\top \mE^\top
= \mE\mE^\top
\label{eq:rotinvar} $
% Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).

@@

\begin{figure}[t]
\centering
\begin{subfigure}[b]{.70\textwidth}
  \centering
  % \includegraphics[width=0.95\linewidth]{figures-error_lines.pdf}
  \includegraphics[height=200px]{figures-error_lines.pdf}
  \caption{}
  \label{fig:3a}
  \label{fig:errorlines}
\end{subfigure}
\begin{subfigure}[b]{.25\textwidth}
  \centering
  % \includegraphics[width=0.65\linewidth]{figures-GeometricLoss.pdf}
  \includegraphics[height=200px]{figures-GeometricLoss.pdf}
  \caption{}
  \label{fig:3b}
  \label{fig:geomloss}
\end{subfigure}
\caption{
  \textbf{(a)} Plot of the losses of the baselines at different iteration numbers.
  The line shows the mean of the graph while the translucent coloring shows the $25^{th}$ to $75^{th}$ percentiles.
  The ROC AUC curves remain fairly consistent while the L1 loss goes noticibly down after more iterations.
  Our method compares to 35-45 iterations of MatchALS, while only having 16 layers and 8 message passes.
  PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
  \textbf{(b)} Training curves with and without Geometric Training loss, described in \ref{eq:geom_cost2}.
  The geometric training loss improves testing performance.
  While the training is higher due to the additional loss terms, the ground truth L1 error is substantially better with the Geometric Loss.
  Best viewed in color.
}
\label{fig:3}
\end{figure}

@@

% \begin{figure}[t]
% \begin{center}
%   % \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
%   \includegraphics[width=0.7\linewidth]{figures-EmbeddingsViz.png}
%   \end{center}
%      \caption{
%          Visualization of the learned embeddings.
%          On the left we have the raw outputs, which are difficult to interpret.
%          In the center, we rotated the features to best match the ground truth for a more interpretable visualization.
%          On the right, we have the ground truth embeddings, given as indicator vectors for which feature in the world the points correspond to.
%      }
%   \label{fig:embeddingsviz}
% \end{figure}
%------------------------------------------------------------------------
\section{Conclusion}

>>>>

\begin{figure}[t]
\begin{subfigure}[b]{.55\linewidth}
  \centering
  \includegraphics[width=0.95\linewidth]{figures-GeometricConsistency-v2.pdf}
  \caption{Illustrated here is an example of how the geometric loss is computed for one feature.}
  \label{fig:1b}
  \label{fig:geoconsist}
\end{subfigure}
\begin{subfigure}[b]{.30\textwidth}
  \centering
  % \includegraphics[width=0.65\linewidth]{figures-GeometricLoss.pdf}
  \includegraphics[height=180px]{figures-GeometricLoss.pdf}
  \caption{}
  \label{fig:3b}
  \label{fig:geomloss}
\end{subfigure}
\caption{
  \textbf{(a)} Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
  The epipolar line is the line of projection of the feature on the first image, projected onto to the second.
  The distance to this line on the second image indicates how likely that point is to correspond geometrically to the original feature.
  There can be false positives along the projected line, as shown by the square feature in the figure, but other points will be eliminated, such as the hexagonal feature.
  Best viewed in color.
  \textbf{(b)} Training curves with and without Geometric Training loss, described in \ref{eq:geom_cost2}.
  The geometric training loss improves testing performance.
  While the training is higher due to the additional loss terms, the ground truth L1 error is substantially better with the Geometric Loss.
  Best viewed in color.
}
\label{fig:1}
\end{figure}

\begin{figure}[t]
\begin{subfigure}[b]{.45\linewidth}
  \centering
  \includegraphics[width=0.95\linewidth]{figures-UniverseOfFeatures-v2.pdf}
  \caption{Illustration of the universe of features.}
  \label{fig:1a}
  \label{fig:universefeatures}
\end{subfigure}%
\begin{subfigure}[b]{.55\linewidth}
  \centering
  \includegraphics[width=0.75\linewidth]{figures-EmbeddingsViz.png}
  % \includegraphics[height=150px]{figures-EmbeddingsViz.png}
  \caption{}
  \label{fig:1b}
  \label{fig:embeddingsviz}
\end{subfigure}
\caption{
  \textbf{(a)} Each feature in each image corresponds to a 3D point in the scene.
  We can construct cycle consistent embeddings of the features by mapping each one to the one-hot vector of its corresponding 3D point.
  While there can be many features, there are fewer 3D points and thus this corresponds to a low rank factorization of the correspondence matrix.
  \textbf{(b)} Visualization of the learned embeddings.
  On the left we have the raw outputs, which are difficult to interpret.
  In the center, we rotated the features to best match the ground truth for a more interpretable visualization.
  On the right, we have the ground truth embeddings, given as indicator vectors for which feature in the world the points correspond to.
  Best viewed in color.
}
\label{fig:1}
\end{figure}

@@

This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
We try to learn vertex embeddings $\mF_V$ to approximate $\mX$ - in other words the final embedding should be an encoding of the universe of features.
As we do not have the ground truth matches $\mM$, we approximate it using the noisy adjacency matrix $\mA$ of our correspondence graph. Thus our loss would be 
\begin{equation}
\mathcal{L}(\mA, \mF_V) = \mathcal{D}(\mA, \mF_V \mF_V^\top)
\end{equation}
Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss. 
Note that because of this formulation, we can determine our embeddings only up to a rotation, as
$ \mE R(\mE R)^\top
= \mE RR^\top \mE^\top
= \mE\mE^\top
\label{eq:rotinvar} $
Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.95\linewidth]{figures-error_lines.pdf}
% \includegraphics[height=200px]{figures-error_lines.pdf}
\label{fig:3}
\label{fig:errorlines}
\caption{
  Plot of the losses of the baselines at different iteration numbers.
  The line shows the mean of the graph while the translucent coloring shows the $25^{th}$ to $75^{th}$ percentiles.
  The ROC AUC curves remain fairly consistent while the L1 loss goes noticibly down after more iterations.
  Our method compares to 35-45 iterations of MatchALS, while only having 16 layers and 8 message passes.
  PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
}
\label{fig:3}
\end{figure}

% 
% \begin{figure}[t]
% \centering
% \begin{subfigure}[b]{.70\textwidth}
%   \centering
%   % \includegraphics[width=0.95\linewidth]{figures-error_lines.pdf}
%   \includegraphics[height=200px]{figures-error_lines.pdf}
%   \caption{}
%   \label{fig:3a}
%   \label{fig:errorlines}
% \end{subfigure}
% \begin{subfigure}[b]{.25\textwidth}
%   \centering
%   % \includegraphics[width=0.65\linewidth]{figures-GeometricLoss.pdf}
%   \includegraphics[height=200px]{figures-GeometricLoss.pdf}
%   \caption{}
%   \label{fig:3b}
%   \label{fig:geomloss}
% \end{subfigure}
% \caption{
%   \textbf{(a)} Plot of the losses of the baselines at different iteration numbers.
%   The line shows the mean of the graph while the translucent coloring shows the $25^{th}$ to $75^{th}$ percentiles.
%   The ROC AUC curves remain fairly consistent while the L1 loss goes noticibly down after more iterations.
%   Our method compares to 35-45 iterations of MatchALS, while only having 16 layers and 8 message passes.
%   PGDDS performs better than us in $L_1$ but we perform similarly in the ROC AUC metric.
%   \textbf{(b)} Training curves with and without Geometric Training loss, described in \ref{eq:geom_cost2}.
%   The geometric training loss improves testing performance.
%   While the training is higher due to the additional loss terms, the ground truth L1 error is substantially better with the Geometric Loss.
%   Best viewed in color.
% }
% \label{fig:3}
% \end{figure}

@@

%------------------------------------------------------------------------
\section{Conclusion}
